---
output:
  pdf_document:
    latex_engine: pdflatex
    extra_dependencies: 
      - booktabs
      - array
      - xcolor
      - colortbl
      - longtable
      - geometry
      - float
params:
  date: !r Sys.Date()
  quote_id: ""
  project_id: ""
  project_title: ""
  project_type: ""
  platform: ""
  table_data: NULL
---

```{r setup, include=FALSE}
# Load required libraries
library(knitr)
library(kableExtra)
```

# WEHI Advanced Genomics Facility (AGF)

**Date:** `r params$date`\
**Quote ID:** `r params$quote_id`\
**Project ID:** `r params$project_id`\
**Project Title:** `r params$project_title`\
**Project Type:** `r params$project_type`\
**Platform:** `r params$platform`



## Invoice Items

```{r echo=FALSE, message=FALSE, warning=FALSE}
knitr::kable(params$table_data, format = "latex", booktabs = TRUE, digits = 2, align = c("l", "c", "c", "r", "r")) %>%
  kable_styling(latex_options = c("striped", "scale_down", "hold_position")) %>%
  kableExtra::column_spec(1, width = "6cm") %>%
  kableExtra::column_spec(2, width = "8cm")

```



## Notes

-   All prices are in **AUD** and exclude **GST**.
-   Cost estimates and quotes are valid for **4 weeks**.
-   Purchase orders and additional price enquiries should be directed to:\
    **Daniela Zalcenstein**\
    [*zalcenstein.d\@wehi.edu.au*](mailto:zalcenstein.d@wehi.edu.au){.email}
